Robustness of MinD oscillation in \emph{Escherichia coli} with diverse cell shapes

### 2014-09-16 paper/paper.tex
minor figure tweak and shift figures around Tested everything on bennet.

@@

\begin{figure*}
  %\includegraphics[width=\textwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-exact/plots/image-plot}
  \includegraphics[width=\textwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-exact/plots/single-image-plot}
  \includegraphics[width=\textwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-full_array/plots/single-image-plot}
  \caption{Contour plot images of the concentration of each protein
    species in a natural pill-shaped bacterium at regular intervals in
    time (one second intervals), with darker regions indicating higher
    concentration. The upper plots shows results from the
    deterministic simulation and the lower shows results from the
    stochastic simulation.  The cells pictured are $4\micron$ in
    length, measured from end to end.  The order of frames is such
    that individual MinD proteins begin at the bottom of the plot (in
    the MinD:ATP state in the cytoplasm), and progress upward until
    they reach the MinE:MinD:ATP membrane-bound complex.  At that
    point, they will spontaneously dissociate into cytoplasmic MinE
    (the top row) and the starting state of cytoplasmic MinD:ADP.  The
    densities plotted are integrated along the axis orthogonal to the
    page, and the color scale is chosen separately for each species
    with black as the maximum value over space and time.  The
    stochastic densities are smeared out over space using a guassians
    approximation developed by Zhang et all~\cite{zhang2007gaussian}}.
  \label{image-p}
\end{figure*}
\section{Naturally Occuring Pill Shaped Cells}

@@

We have made and analyzed movies out of color plots of MinD
concentration that are constructed as those in Figure~\ref{image-p},
integrated along the flattened axis, in which each frame is seperated
in simulation time by a half second. Figure~\ref{randst-plot-ave}
illustrates what is seen in these movies. In his work Mannik presents
arrow plots in which the arrow heads show the location of sequential
MinD maxima within the cell. His plots for his two abnormal cell
shapes are shown in the upper 'experiment' section of
Figure~\ref{randst-plot-ave}.  Following this, we have created plots
that show maxima that are global in space and local in time.  Of these
maxima we only show those which have greater concentration than a
chosen cutoff concentration, and also ignore maxima that appear
temporaly and spatially adjacent to preceding maxima, in order to
stop single spikes from appearing as many adjecent ones.  The overall
effect is to accurately describe what is seen in our movies.

>>>>

\begin{figure*}
  %\includegraphics[width=\textwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-exact/plots/image-plot}
  \includegraphics[width=\textwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-exact/plots/single-image-plot}
  \includegraphics[width=\textwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-full_array/plots/single-image-plot}
  \caption{Contour plot images of the concentration of each protein
    species in a natural pill-shaped bacterium at regular intervals in
    time (one second intervals), with darker regions indicating higher
    concentration. The upper plots shows results from the
    deterministic simulation and the lower shows results from the
    stochastic simulation.  The cells pictured are $4\micron$ in
    length, measured from end to end.  The order of frames is such
    that individual MinD proteins begin at the bottom of the plot (in
    the MinD:ATP state in the cytoplasm), and progress upward until
    they reach the MinE:MinD:ATP membrane-bound complex.  At that
    point, they will spontaneously dissociate into cytoplasmic MinE
    (the top row) and the starting state of cytoplasmic MinD:ADP.  The
    densities plotted are integrated along the axis orthogonal to the
    page, and the color scale is chosen separately for each species
    with black as the maximum value over space and time.  The
    stochastic densities are smeared out over space using a guassians
    approximation developed by Zhang et all~\cite{zhang2007gaussian}}.
  \label{image-p}
\end{figure*}

@@

\section{Naturally Occuring Pill Shaped Cells}

@@

We have made and analyzed movies out of the MinD
concentration that are constructed as those in Figure~\ref{image-p},
integrated along the flattened axis, in which each frame is seperated
in simulation time by a half second. Figure~\ref{randst-plot-ave}
illustrates what is seen in these movies. In his work Mannik presents
arrow plots in which the arrow heads show the location of sequential
MinD maxima within the cell. His plots for his two abnormal cell
shapes are shown in the upper 'experiment' section of
Figure~\ref{randst-plot-ave}.  Following this, we have created plots
that show maxima that are global in space and local in time.  Of these
maxima we only show those which have greater concentration than a
chosen cutoff concentration, and also ignore maxima that appear
temporaly and spatially adjacent to preceding maxima, in order to
stop single spikes from appearing as many adjecent ones.  The overall
effect is to accurately describe what is seen in our movies.
